**From Ecosystems to Genes**: Experimental Test of how Network Structure Shapes the Fitness Landscape

### 2018-09-21 manuscript/manuscript.tex
getting organized

\title{Template and Guidelines for Using \LaTeX{} in \textit{The~American~Naturalist} }

@@

\author{Owen E. Cook$^{1,\ast}$ \\ 
Generic H. Collaborator$^{2,\dag}$ \\ 
Additional Q. Expert$^{3}$}

@@

\noindent{} 1. University of Chicago, Chicago, Illinois 60637;

\noindent{} 2. University of Toronto, Toronto, Ontario M5S 1A5, Canada;

\noindent{} 3. Middle Eastern Technical University, Çankaya, Ankara 06800, Turkey.

\noindent{} $\ast$ Corresponding author; e-mail: amnat@uchicago.edu.

\noindent{} $\dag$ Deceased.

>>>>

\title{Phenotypic evolution is less constrained in complex food webs}

@@

\author{Matthew A. Barbour$^{1,2,\ast}$ \\ 
Christopher J. Greyson-Gaito$^{1,3}$ \\ 
Arezoo Sootodeh$^{3}$ \\
Brendan Lock$^{4} \\
Jordi Bascompte$^{2}}

@@

\noindent{} 1. University of British Columbia, Department of Zoology, Vancouver, British Columbia V6T 1Z4, Canada;

\noindent{} 2. University of Zurich, Department of Evolutionary Biology and Environmental Studies, Winterthurerstrasse 190, 8057 Zurich, Switzerland;

\noindent{} 3. University of Guelph, Department of Integrative Biology, Guelph, Ontario N1G 2W1, Canada;

\noindent{} 3. Humboldt State University, Department of Biological Sciences, Arcata, California 95521, USA.

\noindent{} $\ast$ Corresponding author; e-mail: matthew.barbour@ieu.uzh.ch.

### 2018-09-21 temporary_morgue/Am_Nat_Template.Rnw
getting organized

\begin{document}

@@

>>>>

\begin{document}
\SweaveOpts{concordance=TRUE}

@@

<<echo=FALSE>>=
## Load required libraries ----
library(car)        # for homogeneity of variance test
library(tidyverse)  # for managing data
library(cowplot)    # pretty default ggplots
library(broom)      # for tidying multiple linear models
library(visreg)     # for quick visualizations of model effects
library(viridis)    # for color palette
library(lme4)       # for generalized linear mixed models
library(piecewiseSEM) # for calculating model R-square
library(latex2exp)  # using Latex notation for axes labels

## Load and manage data ----

gall_selection.df <- read_csv("gall_selection_data.csv") %>%
  # convert appropriate variables to characters instead of integers
  mutate(Plant_Position = as.character(Plant_Position),
         Gall_Number = as.character(Gall_Number)) %>%
  unite(Gall_ID, Gall_Number, Gall_Letter, remove = FALSE) %>%

  # subset data for analysis
  filter(phenology == "early", Location == "tree",
         platy > 0 | ectos > 0 | pupa > 0) %>%                  # eliminate unknown sources of mortality
  filter(Treatment.focus == "Ectoparasitoid exclusion" & ectos < 1 | Treatment.focus == "Control") %>% # excluding any larva that were parasitized by an ectoparasitoid in the exclusion experiment.
  mutate(Foodweb = ifelse(Treatment.focus=="Control","Complex","Simple"),
         gall_survival = as.numeric(ifelse(pupa > 0, 1, 0)),
         egg_parasitoid = as.numeric(ifelse(platy > 0, 1, 0)),
         sc.Diam = as.numeric(scale(Gall_Height_mm)), 
         sc.log.Clutch = as.numeric(scale(log(gall_individuals))), 
         sc.log1p.Pref = as.numeric(scale(log1p(Density_per_100_shoots)))) 
dim(gall_selection.df)

table(gall_selection.df$Treatment.focus, gall_selection.df$ectos)

## Create separate datasets for quantifying selection gradients ----
#control_df <- gall_selection.df %>%
#  filter(Treatment.focus == "Control") #%>%
  #mutate(sc.gall_size = as.numeric(scale(Gall_Height_mm)), 
  #       sc.clutch_size = as.numeric(scale(gall_individuals)), 
  #       sc.log.clutch_size = as.numeric(scale(log(gall_individuals))), 
  #       sc.female_preference = as.numeric(scale(Density_per_100_shoots)),
  #       sc.log1p.female_preference = as.numeric(scale(log1p(Density_per_100_shoots))))
#dim(control_df)

#treatment_df <- gall_selection.df %>%
#  filter(Treatment.focus == "Ectoparasitoid exclusion", ectos < 1) #%>%  # excluding any larva that were parasitized by an ectoparasitoid in the exclusion experiment.
#dim(treatment_df)
  #mutate(sc.gall_size = as.numeric(scale(Gall_Height_mm)), 
  #       sc.clutch_size = as.numeric(scale(gall_individuals)), 
  #       sc.log.clutch_size = as.numeric(scale(log(gall_individuals))), 
  #       sc.female_preference = as.numeric(scale(Density_per_100_shoots)),
  #       sc.log1p.female_preference = as.numeric(scale(log1p(Density_per_100_shoots))))

#mean(filter(gall_selection.df, Treatment.focus == "Ectoparasitoid exclusion")$ectos) # less than 3% of larva were parasitized by an ectoparasitoid in the exclusion experiment.

## Custom functions to avoid repetitive code ----

## Test for overdispersion
overdisp_fun <- function(model) {
  ## number of variance parameters in 
  ##   an n-by-n variance-covariance matrix
  vpars <- function(m) {
    nrow(m)*(nrow(m)+1)/2
  }
  model.df <- sum(sapply(VarCorr(model),vpars))+length(fixef(model))
  rdf <- nrow(model.frame(model))-model.df
  rp <- residuals(model,type="pearson")
  Pearson.chisq <- sum(rp^2)
  prat <- Pearson.chisq/rdf
  pval <- pchisq(Pearson.chisq, df=rdf, lower.tail=FALSE)
  c(chisq=Pearson.chisq,ratio=prat,rdf=rdf,p=pval)
}

## Test for multicollinearity (from: https://jonlefcheck.net/2012/12/28/dealing-with-multicollinearity-using-variance-inflation-factors/)
vif.mer <- function (fit) {
    ## adapted from rms::vif

    v <- vcov(fit)
    nam <- names(fixef(fit))

    ## exclude intercepts
    ns <- sum(1 * (nam == "Intercept" | nam == "(Intercept)"))
    if (ns > 0) {
        v <- v[-(1:ns), -(1:ns), drop = FALSE]
        nam <- nam[-(1:ns)]
    }

    d <- diag(v)^0.5
    v <- diag(solve(v/(d %o% d)))
    names(v) <- nam
    v
}

## Transform logit to probability
inverse_logit <- function(x) exp(x)/(1+exp(x))

## Calculate selection gradients following method of Janzen and Stern 1998, Evolution
Beta_avg_grad <- function(.) {
  mean_fitness <- mean(predict(., type = "response")) 
  brackets <- predict(., type = "response") * (1 - predict(., type="response"))
  mean(brackets) * fixef(.)[-1] / mean_fitness ## need to divide by mean fitness to put on relative fitness scale.
}

## Calculate intensity/opportunity for selection
intensity_of_selection <- function(.) {
  mean_fitness <- mean(predict(., type = "response")) # inverse_logit(fixef(update(., .~. -sc.gall_size -sc.clutch_size -sc.female_preference)))
  relative_fitness <- predict(., type = "response") / mean_fitness 
  var(relative_fitness)
}

## Compute the matrix describing the curvature of the fitness landscape
curvature_fitness.landscape <- function(gammas, # matrix of nonlinear and correlational selection gradients 
                                        betas){ # vector of directional selection gradients
  gammas - betas %*% t(betas)
}

## Bootstrap fitness estimates
bootstrap_fitness <- function(logistic_model, fixed_effects, newdata, bootstraps, intervals=c(0.025,0.975)){
  model_matrix <- model.matrix(formula(fixed_effects), newdata)

  # Absolute fitness
  get_absolute_fitness <- function(.) inverse_logit(model_matrix %*% fixef(.))

  if(is.null(bootstraps) == FALSE){
    get_bootstraps_absolute_fitness <-bootMer(logistic_model, FUN = get_absolute_fitness, nsim=bootstraps, parallel="multicore", ncpus=32)

   get_intervals_absolute_fitness <- apply(get_bootstraps_absolute_fitness$t, 2, function(x) x[order(x)][c(round(bootstraps*intervals[1],0),round(bootstraps*intervals[2],0))])

  absolute_fitness_df <- data.frame(newdata, 
                    average = get_absolute_fitness(logistic_model), 
                    lower = get_intervals_absolute_fitness[1, ],
                    upper = get_intervals_absolute_fitness[2, ],
                    t(get_bootstraps_absolute_fitness$t))
  } else {
    absolute_fitness_df <- data.frame(newdata, 
                    average = get_absolute_fitness(logistic_model))
  }

  # Relative fitness
  get_relative_fitness <- function(.) get_absolute_fitness(.)/mean(get_absolute_fitness(.))

  if(is.null(bootstraps) == FALSE){
    get_bootstraps_relative_fitness <-bootMer(logistic_model, FUN = get_relative_fitness, nsim=bootstraps, parallel="multicore", ncpus=32)

  get_intervals_relative_fitness <- apply(get_bootstraps_relative_fitness$t, 2, function(x) x[order(x)][c(round(bootstraps*intervals[1],0),round(bootstraps*intervals[2],0))])

  relative_fitness_df <- data.frame(newdata, 
                    average = get_relative_fitness(logistic_model), 
                    lower = get_intervals_relative_fitness[1, ],
                    upper = get_intervals_relative_fitness[2, ],
                    t(get_bootstraps_relative_fitness$t))
  } else {
      relative_fitness_df <- data.frame(newdata, 
                    average = get_relative_fitness(logistic_model))
  }

  # Organize data
  return(list(absolute_fitness = absolute_fitness_df, relative_fitness = relative_fitness_df))
}

## Number of bootstrap replicates
n_boots_analysis <- 30
n_boots_plots <- 100
@

bootstraps $=Sexpr{sqrt(2)}$

### 2018-09-21 temporary_morgue/Am_Nat_Template.tex
getting organized

\begin{document}
\SweaveOpts{concordance=TRUE}

@@

<<echo=FALSE>>=
## Load required libraries ----
library(car)        # for homogeneity of variance test
library(tidyverse)  # for managing data
library(cowplot)    # pretty default ggplots
library(broom)      # for tidying multiple linear models
library(visreg)     # for quick visualizations of model effects
library(viridis)    # for color palette
library(lme4)       # for generalized linear mixed models
library(piecewiseSEM) # for calculating model R-square
library(latex2exp)  # using Latex notation for axes labels

## Load and manage data ----

gall_selection.df <- read_csv("gall_selection_data.csv") %>%
  # convert appropriate variables to characters instead of integers
  mutate(Plant_Position = as.character(Plant_Position),
         Gall_Number = as.character(Gall_Number)) %>%
  unite(Gall_ID, Gall_Number, Gall_Letter, remove = FALSE) %>%

  # subset data for analysis
  filter(phenology == "early", Location == "tree",
         platy > 0 | ectos > 0 | pupa > 0) %>%                  # eliminate unknown sources of mortality
  filter(Treatment.focus == "Ectoparasitoid exclusion" & ectos < 1 | Treatment.focus == "Control") %>% # excluding any larva that were parasitized by an ectoparasitoid in the exclusion experiment.
  mutate(Foodweb = ifelse(Treatment.focus=="Control","Complex","Simple"),
         gall_survival = as.numeric(ifelse(pupa > 0, 1, 0)),
         egg_parasitoid = as.numeric(ifelse(platy > 0, 1, 0)),
         sc.Diam = as.numeric(scale(Gall_Height_mm)), 
         sc.log.Clutch = as.numeric(scale(log(gall_individuals))), 
         sc.log1p.Pref = as.numeric(scale(log1p(Density_per_100_shoots)))) 
dim(gall_selection.df)

table(gall_selection.df$Treatment.focus, gall_selection.df$ectos)

## Create separate datasets for quantifying selection gradients ----
#control_df <- gall_selection.df %>%
#  filter(Treatment.focus == "Control") #%>%
  #mutate(sc.gall_size = as.numeric(scale(Gall_Height_mm)), 
  #       sc.clutch_size = as.numeric(scale(gall_individuals)), 
  #       sc.log.clutch_size = as.numeric(scale(log(gall_individuals))), 
  #       sc.female_preference = as.numeric(scale(Density_per_100_shoots)),
  #       sc.log1p.female_preference = as.numeric(scale(log1p(Density_per_100_shoots))))
#dim(control_df)

#treatment_df <- gall_selection.df %>%
#  filter(Treatment.focus == "Ectoparasitoid exclusion", ectos < 1) #%>%  # excluding any larva that were parasitized by an ectoparasitoid in the exclusion experiment.
#dim(treatment_df)
  #mutate(sc.gall_size = as.numeric(scale(Gall_Height_mm)), 
  #       sc.clutch_size = as.numeric(scale(gall_individuals)), 
  #       sc.log.clutch_size = as.numeric(scale(log(gall_individuals))), 
  #       sc.female_preference = as.numeric(scale(Density_per_100_shoots)),
  #       sc.log1p.female_preference = as.numeric(scale(log1p(Density_per_100_shoots))))

#mean(filter(gall_selection.df, Treatment.focus == "Ectoparasitoid exclusion")$ectos) # less than 3% of larva were parasitized by an ectoparasitoid in the exclusion experiment.

## Custom functions to avoid repetitive code ----

## Test for overdispersion
overdisp_fun <- function(model) {
  ## number of variance parameters in 
  ##   an n-by-n variance-covariance matrix
  vpars <- function(m) {
    nrow(m)*(nrow(m)+1)/2
  }
  model.df <- sum(sapply(VarCorr(model),vpars))+length(fixef(model))
  rdf <- nrow(model.frame(model))-model.df
  rp <- residuals(model,type="pearson")
  Pearson.chisq <- sum(rp^2)
  prat <- Pearson.chisq/rdf
  pval <- pchisq(Pearson.chisq, df=rdf, lower.tail=FALSE)
  c(chisq=Pearson.chisq,ratio=prat,rdf=rdf,p=pval)
}

## Test for multicollinearity (from: https://jonlefcheck.net/2012/12/28/dealing-with-multicollinearity-using-variance-inflation-factors/)
vif.mer <- function (fit) {
    ## adapted from rms::vif

    v <- vcov(fit)
    nam <- names(fixef(fit))

    ## exclude intercepts
    ns <- sum(1 * (nam == "Intercept" | nam == "(Intercept)"))
    if (ns > 0) {
        v <- v[-(1:ns), -(1:ns), drop = FALSE]
        nam <- nam[-(1:ns)]
    }

    d <- diag(v)^0.5
    v <- diag(solve(v/(d %o% d)))
    names(v) <- nam
    v
}

## Transform logit to probability
inverse_logit <- function(x) exp(x)/(1+exp(x))

## Calculate selection gradients following method of Janzen and Stern 1998, Evolution
Beta_avg_grad <- function(.) {
  mean_fitness <- mean(predict(., type = "response")) 
  brackets <- predict(., type = "response") * (1 - predict(., type="response"))
  mean(brackets) * fixef(.)[-1] / mean_fitness ## need to divide by mean fitness to put on relative fitness scale.
}

## Calculate intensity/opportunity for selection
intensity_of_selection <- function(.) {
  mean_fitness <- mean(predict(., type = "response")) # inverse_logit(fixef(update(., .~. -sc.gall_size -sc.clutch_size -sc.female_preference)))
  relative_fitness <- predict(., type = "response") / mean_fitness 
  var(relative_fitness)
}

## Compute the matrix describing the curvature of the fitness landscape
curvature_fitness.landscape <- function(gammas, # matrix of nonlinear and correlational selection gradients 
                                        betas){ # vector of directional selection gradients
  gammas - betas %*% t(betas)
}

## Bootstrap fitness estimates
bootstrap_fitness <- function(logistic_model, fixed_effects, newdata, bootstraps, intervals=c(0.025,0.975)){
  model_matrix <- model.matrix(formula(fixed_effects), newdata)

  # Absolute fitness
  get_absolute_fitness <- function(.) inverse_logit(model_matrix %*% fixef(.))

  if(is.null(bootstraps) == FALSE){
    get_bootstraps_absolute_fitness <-bootMer(logistic_model, FUN = get_absolute_fitness, nsim=bootstraps, parallel="multicore", ncpus=32)

   get_intervals_absolute_fitness <- apply(get_bootstraps_absolute_fitness$t, 2, function(x) x[order(x)][c(round(bootstraps*intervals[1],0),round(bootstraps*intervals[2],0))])

  absolute_fitness_df <- data.frame(newdata, 
                    average = get_absolute_fitness(logistic_model), 
                    lower = get_intervals_absolute_fitness[1, ],
                    upper = get_intervals_absolute_fitness[2, ],
                    t(get_bootstraps_absolute_fitness$t))
  } else {
    absolute_fitness_df <- data.frame(newdata, 
                    average = get_absolute_fitness(logistic_model))
  }

  # Relative fitness
  get_relative_fitness <- function(.) get_absolute_fitness(.)/mean(get_absolute_fitness(.))

  if(is.null(bootstraps) == FALSE){
    get_bootstraps_relative_fitness <-bootMer(logistic_model, FUN = get_relative_fitness, nsim=bootstraps, parallel="multicore", ncpus=32)

  get_intervals_relative_fitness <- apply(get_bootstraps_relative_fitness$t, 2, function(x) x[order(x)][c(round(bootstraps*intervals[1],0),round(bootstraps*intervals[2],0))])

  relative_fitness_df <- data.frame(newdata, 
                    average = get_relative_fitness(logistic_model), 
                    lower = get_intervals_relative_fitness[1, ],
                    upper = get_intervals_relative_fitness[2, ],
                    t(get_bootstraps_relative_fitness$t))
  } else {
      relative_fitness_df <- data.frame(newdata, 
                    average = get_relative_fitness(logistic_model))
  }

  # Organize data
  return(list(absolute_fitness = absolute_fitness_df, relative_fitness = relative_fitness_df))
}

## Number of bootstrap replicates
n_boots_analysis <- 30
n_boots_plots <- 100
@

>>>>

\usepackage{Sweave}
\begin{document}
\input{Am_Nat_Template-concordance}

@@

\begin{Schunk}
\begin{Soutput}
[1] 1285   25
\end{Soutput}
\begin{Soutput}
                             0   1
  Control                  535 168
  Ectoparasitoid exclusion 582   0
\end{Soutput}
\end{Schunk}

### 2018-09-21 temporary_morgue/GRC_2018_test.Rmd
getting organized

---
title: "From ecosystems to genes: an experimental test of how network structure affects the fitness landscape"
output: 
  revealjs::revealjs_presentation:
    theme: default
    transition: fade
    self_contained: true

---

# Scaling From Genes to Ecosystems

@@

# Framework for Linking Ecosystems to Genes?

Image flipping network structure to affecting a species to visualize how network structure could contrain or facilitate phenotypic and genetic change

At the same time, I think it's equally important to start thinking about how network structure feedsback to constrain or facilitate evolutionary change. This is what I want to spend my time discussing today

# Fitness Landscape Unifies Ecology & Evolution

```{r McPeek Fig 1, out.width = "400px"}
knitr::include_graphics("McPeek_Fig_1.png")
```

@@

# Inferring the Fitness Landscape

$$w = z$$

Nice theory that links individual selection surfaces to the fitness landscape (Arnold 2003)

We can then use standard tools to estimate the local shape of the fitness landscape. e.g. Slope = Beta (same as selective surface); Curvature is equal to Gamm - Beta*Transpose(Beta)

# Willow Garden

```{r Garden pic, echo=FALSE, out.width = "400px"}
knitr::include_graphics("willow_garden_2011-enhanced-1226.jpeg")
```

Common garden was located at Humboldt Bay National Wildlife Refuge in northern California, and it consisted of 26 genotypes that were sampled from the local willow population.

# Experimental Manipulation of Network Structure

Photos illustrating how I manipulated the food web and what the resulting community looks like.

# Measuring Gall Phenotypes

1. Gall Diameter (mm)
2. Clutch size (no. larva per gall)
3. Oviposition preference (no. larva per 100 shoots)

Include an image next to these to illustrate what each of these phenotypes mean. Use the image that has the arrows pointing to measurment of gall diameter and to individual larva

# Quantifying the Fitness Landscape

# Absolute Fitness

```{r Univariate Landscapes}
library(qwraps2)
library(cowplot)

@@

First draw attention to the mean differences and then to the slopes (the different components)

Build up each of the figures

```{r}
library(qwraps2)
library(cowplot)
library(tidyverse)

uni_breaks <- c(0.1,0.5,1)

# Gall size 
AF_uni_size <- bind_rows(mutate(RF_treatment_gall_size$absolute_fitness, Food_Web = "Simple"), 
          mutate(RF_control_gall_size$absolute_fitness, Food_Web = "Complex")) %>%
  select(-sc.clutch_size, -sc.female_preference) %>%
  gather(ID, absolute_fitness, -sc.gall_size, -Food_Web) %>%
  mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>% 
  ggplot(., aes(x=sc.gall_size, y=absolute_fitness, group=interaction(ID,Food_Web), color=Food_Web, alpha=ID_group, size=ID_group)) +
  geom_line() +
  scale_alpha_manual(values=c(1,0.2), guide=FALSE) +
  scale_size_manual(values=c(1.5,0.25), guide=FALSE) +
  xlab("Gall diameter (SDs)") +
  ylab("Population mean fitness") +
  scale_color_manual(values = treatment_colors, name = "Food web") +
  scale_y_log10(breaks=uni_breaks, labels=uni_breaks) + annotation_logticks(sides = "l") +
  coord_cartesian(ylim=c(0.07,1))
#AF_uni_size
  #scale_y_continuous(breaks = AF_gradient_scale, limits = c(min(AF_gradient_scale), max(AF_gradient_scale)), trans = "log")

# Clutch size
AF_uni_clutch <- bind_rows(mutate(RF_treatment_clutch_size$absolute_fitness, Food_Web = "Simple"), 
          mutate(RF_control_clutch_size$absolute_fitness, Food_Web = "Complex")) %>%
  select(-sc.gall_size, -sc.female_preference) %>%
  gather(ID, absolute_fitness, -sc.clutch_size, -Food_Web) %>%
  mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>% 
  ggplot(., aes(x=sc.clutch_size, y=absolute_fitness, group=interaction(ID,Food_Web), color=Food_Web, alpha=ID_group, size=ID_group)) +
  geom_line() +
  scale_alpha_manual(values=c(1,0.2), guide=FALSE) +
  scale_size_manual(values=c(1.5,0.25), guide=FALSE) +
  xlab("Clutch size (SDs)") +
  ylab("Population mean fitness") +
  scale_color_manual(values = treatment_colors, name = "Food web") +
  scale_y_log10(breaks=uni_breaks, labels=uni_breaks) + annotation_logticks(sides = "l") +
  coord_cartesian(ylim=c(0.07,1))
  #scale_y_continuous(breaks = AF_gradient_scale, limits = c(min(AF_gradient_scale), max(AF_gradient_scale)), trans = "log")

# Female preference
AF_uni_pref <- bind_rows(mutate(RF_treatment_female_preference$absolute_fitness, Food_Web = "Simple"), 
          mutate(RF_control_female_preference$absolute_fitness, Food_Web = "Complex")) %>%
  select(-sc.gall_size, -sc.clutch_size) %>%
  gather(ID, absolute_fitness, -sc.female_preference, -Food_Web) %>%
  mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>% 
  ggplot(., aes(x=sc.female_preference, y=absolute_fitness, group=interaction(ID,Food_Web), color=Food_Web, alpha=ID_group, size=ID_group)) +
  geom_line() +
  scale_alpha_manual(values=c(1,0.2), guide=FALSE) +
  scale_size_manual(values=c(1.5,0.25), guide=FALSE) +
  xlab("Female preference (SDs)") +
  ylab("Population mean fitness") +
  scale_color_manual(values = treatment_colors, name = "Food web") +
  scale_y_log10(breaks=uni_breaks, labels=uni_breaks) + annotation_logticks(sides = "l") +
  coord_cartesian(ylim=c(0.07,1))
  #scale_y_continuous(breaks = AF_gradient_scale, limits = c(min(AF_gradient_scale), max(AF_gradient_scale)), trans = "log")

# Get legend
AF_uni_legend <- get_legend(AF_uni_size)

# Make plots
AF_uni_plots <- plot_grid(AF_uni_size + theme(legend.position = "none"), 
                       AF_uni_clutch + theme(legend.position = "none", 
                                          axis.title.y = element_blank(), axis.text.y = element_blank()),
                       AF_uni_pref + theme(legend.position = "none", 
                                        axis.title.y = element_blank(), axis.text.y = element_blank()),
                       labels = "AUTO", ncol = 3, align='hv')

#AF_gradients <- ggdraw(AF_uni_plots) + draw_grob(AF_uni_legend, x = 0.8, y=0)
#AF_gradients
AF_uni_plots
save_plot("FL_1D.pdf", AF_uni_plots, base_height = 6.5, base_width = 8)
```

```{r Multivariate Absolute Fitness Landscapes, echo=FALSE, message=FALSE, warning=FALSE}
library(viridis)

my_breaks <- c(0.2,0.4,0.6,0.8)

# Size x Preference
AF_plot_size.x.preference <- bind_rows(mutate(RF_treatment_size.x.preference$absolute_fitness, Food_Web = "Simple"), 
          mutate(RF_control_size.x.preference$absolute_fitness, Food_Web = "Complex")) %>%
  ggplot(., aes(x=sc.gall_size, y=sc.female_preference, fill=average)) +
  geom_raster() +
  facet_wrap(~Food_Web) +
  xlab("Gall diameter (SDs)") +
  ylab("Female preference (SDs)") +
  scale_fill_viridis(name = "Population\nmean fitness", trans="log", breaks = my_breaks, labels = my_breaks, limits = c(0.1,1)) # limits = c(AF_range$min, AF_range$max),

# Size x Clutch
AF_plot_size.x.clutch <- bind_rows(mutate(RF_treatment_size.x.clutch$absolute_fitness, Food_Web = "Simple"), 
          mutate(RF_control_size.x.clutch$absolute_fitness, Food_Web = "Complex")) %>%
  ggplot(., aes(x=sc.gall_size, y=sc.clutch_size, fill=average)) +
  geom_raster() +
  facet_wrap(~Food_Web) +
  xlab("Gall diameter (SDs)") +
  ylab("Clutch size (SDs)") +
  scale_fill_viridis(name = "Population\nmean fitness", trans="log", breaks = my_breaks, labels = my_breaks, limits = c(0.1,1)) # limits = c(AF_range$min, AF_range$max),

# Clutch x Preference
AF_plot_clutch.x.preference <- bind_rows(mutate(RF_treatment_clutch.x.preference$absolute_fitness, Food_Web = "Simple"), 
          mutate(RF_control_clutch.x.preference$absolute_fitness, Food_Web = "Complex")) %>%
  ggplot(., aes(x=sc.female_preference, y=sc.clutch_size, fill=average)) +
  geom_raster() +
  facet_wrap(~Food_Web) +
  xlab("Female preference (SDs)") +
  ylab("Clutch size (SDs)") +
  scale_fill_viridis(name = "Population\nmean fitness", trans="log", breaks = my_breaks, labels = my_breaks, limits = c(0.1,1)) # limits = c(AF_range$min, AF_range$max),

# Get legend
AF_landscape_legend <- get_legend(AF_plot_size.x.preference)

# Format plots
AF_landscape_plots <- plot_grid(
  AF_plot_size.x.clutch + theme(legend.position = "none", axis.title.x = element_blank()),
  AF_plot_clutch.x.preference + theme(legend.position = "none", axis.title.y = element_blank()),
  AF_plot_size.x.preference + theme(legend.position = "none"), 
  nrow=2, align="hv", labels = "AUTO")
AF_landscape_2d <- ggdraw(AF_landscape_plots) + draw_grob(AF_landscape_legend, x = 0.7, y=-0.2)
AF_landscape_2d
#save_plot("AF_landscapes_2d.png", AF_landscape_2d, base_height=6, base_width = 8)
save_plot("FL_2D.pdf", AF_landscape_2d, base_height=6, base_width = 8)
```

# Relative Fitness

- Univariate landscapes

Now show the same univariate plots but with the relative fitness on the y-axis.

First put the absolute landscape next to relative fitness to show the link between the two, then show the rest of the landscapes.

# Multivariate Perspective

Here is a different representation of these univariate landscapes.

Describe the axes for the figures.

# Conclusions

- Natural selection is stronger, yet less constrained in the complex food web.

# Open Questions

-

# Note

in presentation for GRC - emphasize also that the opportunity for selection is X% higher in the complex vs. simple environment, although that may be an artifact of the study (excluding parasitoids reduced mean fitness, which is likely why selection on gall diameter is twice as much).

>>>>

---
title: "**From Ecosystems to Genes**: Experimental Test of how Network Structure Shapes the Fitness Landscape"
output: 
  revealjs::revealjs_presentation:
    transition: fade
    self_contained: false
    reveal_plugins: ["notes"]
---

## Scaling from Genes to Ecosystems

@@

^Note: Blah blah blah

## Slide with Bullets

```{r Slide with Bullets Header}
cat("
<style>
h1 {
   color: red;
}
</style>
")
```

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Code and Output

```{r}
summary(cars)
```

## Slide with Plot

```{r, echo=FALSE}
plot(cars)
```

## Fitness Landscape Unifies Ecology & Evolution

```{r McPeek Fig 1, out.width = "400px", echo=FALSE}
knitr::include_graphics("McPeek_Fig_1.png")
```

@@

## Univariate

```{r Univariate Landscapes, echo=FALSE, message=FALSE}
library(qwraps2)
library(cowplot)

@@
